Demographic inference using the SFS with Moments and Demes

### 2025-03-18 chapter/paper.tex
get at least a bit of writing going

@@

\abstract{
Placeholder
}

@@

@@

Incluce here general ideas about the strengths and weaknesses of various approaches
in population genetic inference, including when using the SFS.

Challenges in finding local/global optima. Challenges in exploring parameter space.

>>>>

\newcommand{\moments}{\texttt{moments}\xspace}

@@

\begin{abstract}
    Placeholder
\end{abstract}

@@

The genetic composition within a sample of individuals is shaped by their
genome biology and evolutionary history. Variation resulting from this history
is fully described by the ancestral relationships among samples at each locus
in the genome and how they change along a chromosome due to recombination (that
is, information stored in the Ancestral Recombination Graph [cites]). However,
the ARG can be large and unwieldy, and methods for reconstructing history
directly from the ARG, while showing promise [cite], are in their infancy and
so far limited in application and scalability [cite]. Instead, evolutionary
inference using informative summaries provides a tractable and powerful
alternative for learning parameters of population history, natural selection and
genome biology.

One such summary that has seen wide use is the site frequency spectrum (SFS),
which stores the counts (observed or expected) of alleles carried by a given
number of genomes in a set of samples. Like any summary of the data, the SFS
discards information relative to the ARG -- in this case, loci are treated
independently so that haplotypic information is lost. Nonetheless, a great deal
can be learned from the

@@

\begin{enumerate}
    \item Incluce here general ideas about the strengths and weaknesses of
        various approaches in population genetic inference, including when
        using the SFS.
    \item Challenges in finding local/global optima.
    \item Challenges in exploring parameter space.
    \item Gene dense vs gene sparse genomic architectures among species.
\end{enumerate}
